Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-05-30 paper/src/dis.tex
Add ref to new dwarf AGN paper

Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario. \citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P}.

>>>>

Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario. \citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P,2024arXiv240518685M}.
